---
title: "smart_cities_template - for the 6 themes"
author: "AB"
date: "20 April 2016"
output: html_document
---
#Smart Cities Data - Template
## Introduction
This analysis etc etc etc


```{r, include=F, echo=F}
library(foreign)
library(ggplot2)
library(Hmisc)
library(gridExtra)


setwd("/home/ab/Documents/MBD/data_mining/assignment3/data")
list.files()
df1 = spss.get("SPSS_Smart_Cities.sav" ) # Changed form read.spss to spss.get. This gives us the survey topics directly.
df = as.data.frame(df1)

levels(df$p1.1) <- c(levels(df$p1.1), "Si, Pero no") 
df$p1.1[df$p1.1 == "Lo he escuchado pero desconozco su significado"] <- "Si, Pero no"  # Change long answer to shorter answer to better fit visualizations. 
levels(df$p1.1) <- c(levels(df$p1.1), "Si, Pero no") 
df$p1.1 = factor(df$p1.1)

levels(df$ClaseSocial) = c("Alta","Media Alta","Media","Media Baja","Baja")

```

##Exploritory Analysis
###Overview
In total, there were 1810 respondants from 14 cities in Spain.
Surveys were taken from between the 14th of May 2015 and the 26th of May 2015. 

```{r,include=F, echo=F}
length(df)
table(df$ciudadq)
sort(table(df$yyyymmdd))
```

### Basic Demographics
Participants were asked some basic demographic questions such as gender, age and social class.
The participants were nearly 50/50 split by gender, with 604 being men and 601 being women.
By age, the participants fall evenly into the three age groups.
* 401 were between 18 and 29 years
* 402 were between 30 and 45
* 402 were between 45 and 60.

```{r,include=F, echo=F}
table(df$sexo)
table(df$edad)
```

Social Class was less even than the other deomographic groups. Chart 1 shows the count by identified social class.
```{r,echo=F,fig.width=10}
qplot(df$ClaseSocial, main = "Chart 1 - Respondents by Class")
```

##Introductory Questions
###Knowledge about Smart Cities
Respondents were first asked if they knew the smart city concept. The results indicate that more respondents knew about the smart city concept than those that don't. However, we see in chart 2, that many respondents knew about the concept are undertain what it means excatly. People know about the idea but lack an understanding about the details.

```{r,echo = F,fig.width=10}
know = ggplot(df, aes(x=p1.1)) + geom_bar(fill="grey", colour="black") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
know + labs(title = "Chart 2 - Knowledge of smart cities, number of respondents") 
```

###Knowledge about Smart Cities by Gender
When we break down the knowledge about smart cities by gender, we see that more men identified as being knowledgable about smart cities when compared to women. Women appear to be either be less knowledgable or more willing to admit that they do not know about the concept (Chart 3). 

```{r,echo=F,fig.width=10}
plot(df$sexo,df$p1.1, xlab = "Gender", ylab = "Knowledge", main = "Chart 3 - Knowledge of smart cities, number of respondents by Gender")
```

###Knowledge about Smart Cities by Age
Segmenting by age group, we see that more people in oldest age group admitted to not knowing about the smart city concept. Less than 40 percent of participants in the 46 to 60 year age group said their knew about smart cities. The two other groups, between 18 and 29 and between 30 and 45 had similar proportions in their answers (Chart 4).

```{r,echo=F,fig.width=10}
plot(df$edad,df$p1.1, xlab = "Gender", ylab = "Knowledge", main = "Chart 4 - Knowledge of smart cities, number of respondents by Age")
```

###Knowledge about Smart Cities by Class
By class, we see that the higher classes reported more yes' when compared to lower classes. Over 50 percent of participants in the Alta Class said their knew about smart cities. While less than 30 percent reported the same response in the Media Baja and Baja Classes (Chart 5).

```{r,echo=F,fig.width=10}
plot(df$ClaseSocial,df$p1.1, xlab = "Gender", ylab = "Knowledge", main = "Chart 5 - Knowledge of smart cities, number of respondents by Class")
```


## Importance of Smart City initiatives in Mobility
### Overview
Participants were asked their opinion on howimportant six specific improvement were to them. They were asked to answer 1 if the improvement is not important and answer 5 if the initiative is Very Important. The six improvements were
* Intelligent Public Transport
* Automated Vehicle Access Restrictions and Tolls
* Intelligent Traffic Management
* Intelligent Fleet Management
* Parking Intelligence
* Electric Vehicle Infrastructure

Each improvement included examples of what this improvement might mean. 

###Responses
```{r, echo = F, include=F}
#Create the sum of scores for transport
df$df_trans_sum = (as.numeric(df$p2.2.2.it1.Slice) +
                  as.numeric(df$p2.2.2.it2.Slice) +
                  as.numeric(df$p2.2.2.it3.Slice) +
                  as.numeric(df$p2.2.2.it4.Slice) +
                  as.numeric(df$p2.2.2.it5.Slice) + 
                  as.numeric(df$p2.2.2.it6.Slice))

df$df_trans_ave = (as.numeric(df$p2.2.2.it1.Slice) +
                  as.numeric(df$p2.2.2.it2.Slice) +
                  as.numeric(df$p2.2.2.it3.Slice) +
                  as.numeric(df$p2.2.2.it4.Slice) +
                  as.numeric(df$p2.2.2.it5.Slice) + 
                  as.numeric(df$p2.2.2.it6.Slice)) / 6

```

Mobility and transport was identified as being mostly important to respondents. Chart 6 below shows the histogram of the response scores, with a median of 3.8. 
```{r, echo=F}
inte_hist = ggplot(df, aes(x = df_trans_ave)) +  geom_bar() + ggtitle("Chart 6 - Average Responses to Mobility Questions") + xlab("Importance") + ylab("Count")  + geom_vline(show.legend = TRUE,xintercept=median(df$df_trans_ave), linetype = "longdash")
inte_hist 
```

Charts 7 to 12 below show the frequency of responses for each importance level. They indicate that Intelligent Public Transport and Electric Vehicle Infrastructure are the most important mobility initiatives. On the contrary, initiatives focused on Access Restrictions appear to be the least popular. 
```{r,echo=F,fig.width=10}
inte_tr1 = ggplot(df, aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 7 - Responses to Intelligent Public Transport") + xlab("Importance") + ylab("Percent")

inte_tr2 = ggplot(df, aes(x = p2.2.2.it2.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 8 - Responses to Access Restrictions") + xlab("Importance") + ylab("Percent")

inte_tr3 = ggplot(df, aes(x = p2.2.2.it3.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 9 - Responses to Intelligent Traffic Management") + xlab("Importance") + ylab("Percent")

inte_tr4 = ggplot(df, aes(x = p2.2.2.it4.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 10 - Responses to Intelligent Fleet Management") + xlab("Importance") + ylab("Percent")

inte_tr5 = ggplot(df, aes(x = p2.2.2.it5.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 11 - Responses to Parking Intelligence") + xlab("Importance") + ylab("Percent")

inte_tr6 = ggplot(df, aes(x = p2.2.2.it6.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 12 - Responses to Electric Vehicle Infrastructure") + xlab("Importance") + ylab("Percent")

grid.arrange(inte_tr1, inte_tr2,inte_tr3,inte_tr4,inte_tr5,inte_tr6, ncol=2)

```

##Intelligent Public Transport
Participants were asked their view on important intelligent public transport. Intelligent public transport priority signals for public transport, integrated fares between bus, metro, suburban, realtime incidents and frequency services digital advice to travelers. Therefore, it looks at using technology to prioritise public transport and to intelligently notify users of public transport schedules. 

###Intelligent Public Transport by Gender
More female respondents beleived improvements in intelligent public transport was very important. Charts 13 and 14 show that forty five percent of female respondents rated intelligent public transport as very important. No females indicated intelligent public transport was not important. 
```{r,echo=F}
inte_tr1_gm = ggplot(subset(df,sexo == 'Hombre'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 13 - Male Responses to Intelligent Public Transport") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_gf = ggplot(subset(df,sexo == 'Mujer'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 14 - Female Responses to Intelligent Public Transport") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

grid.arrange(inte_tr1_gm, inte_tr1_gf, ncol=2)
```

```{r}
ggplot(df, aes(factor(sexo), as.numeric(p2.2.2.it1.Slice))) + geom_boxplot() + ggtitle("Do we include this? It is catagorical")
```

######Intelligent Public Transport by Gender - Statistical Difference
This apparent difference is now tested statistically with the aim of determining if the difference in the sample can be hypothesised against the population as a whole.

The T-Test below indicates that there is difference in the mean scores between men and women over the population. This indicates that men and women differ in their opinion of the importance of Intelligent Public Transport.

The T-Test's parameters are
* The Null Hypothesis states that there is no difference between the mean score for men and women.
* The Alternative Hypothesis is that there is a difference between the mean score for men and women.
* The Confidence internal is 95%.

The resulting P-Value is 0.000172 which is under our critical. Therefore we reject the null hypothesis that the means are the same. 
```{r,echo=F}
inte_tr5_g_ttest = t.test(as.numeric(df$p2.2.2.it1.Slice)~df$sexo)
inte_tr5_g_ttest$p.value
```


###Intelligent Public Transport by Age
Older respondents indicated that the intelligent public transport was very important more than younger respondents. Charts 15 to 17 show that just over forty five percent of  respondents between the ages of 46 abd 60 rated intelligent public transport as very important. This is well above the 33 percent of respondents from the 18 to 29 age group.  

```{r,echo=F}
inte_tr1_a1 = ggplot(subset(df,edad == 'De 18 a 29 años'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 15 - Responses to Intelligent Public Transport, \n 18-29 years") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_a2 = ggplot(subset(df,edad == 'De 30 a 45 años'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 16 -  - Responses to Intelligent Public Transport, \n  30-45 years") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_a3 = ggplot(subset(df,edad == 'De 46 a 60 años'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 17 - Responses to Intelligent Public Transport, \n  46-60 years") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

grid.arrange(inte_tr1_a1, inte_tr1_a2,inte_tr1_a3, ncol=3)
```

```{r}
ggplot(df, aes(factor(edad), as.numeric(p2.2.2.it1.Slice))) + geom_boxplot() + ggtitle("Do we include this? It is catagorical")
```

######Intelligent Public Transport by Age - Statistical Difference
This obvious difference is now tested statistically with the aim of determining if the difference in the sample can be hypothesised against the population as a whole.

The ANOVA below indicates that there is difference in the mean scores between the age groups over the population. This indicates that the person's age influences their opinion of the importance of Intelligent Public Transport.

The ANOVA parameters were
* The Null Hypothesis states that there is no difference between the mean score for each age group.
* The Alternative Hypothesis is that there is a difference between the mean score for each age group.
* The Confidence internal is 95%.

The resulting P-Value is 3.57e-06 is under our critical. Therefore we reject the null hypothesis that the means are the same.
```{r,echo=F}
inte_tr5_e_aov = aov(as.numeric(df$p2.2.2.it1.Slice)~df$edad)
summary(inte_tr5_e_aov)
```


###Intelligent Public Transport by Class
Across the classes, there were only small differences in opinion about the importance of intelligent public transport. Charts 18 to 22 show that about forty percent of respondents in the Upper, Upper Middle, Middle and Lower Middles clases rated intelligent public transport as very important. The outlier is the lower class. The percetnage results in this class group is likely influenced by the low number of total respondents in this group (15 respondents). 

```{r,echo=F}
inte_tr1_cla = ggplot(subset(df,ClaseSocial == 'Alta'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 18 - Responses to Intelligent Public Transport, \n Upper Class") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_cma = ggplot(subset(df,ClaseSocial == 'Media Alta'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 19 - Responses to Intelligent Public Transport, \n Upper Middle Class") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_cm = ggplot(subset(df,ClaseSocial == 'Media'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 20 - Responses to Intelligent Public Transport, \n Middle Class") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_cmb = ggplot(subset(df,ClaseSocial == 'Media Baja'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 21 - Responses to Intelligent Public Transport, \n Middle Lower Class") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

inte_tr1_b = ggplot(subset(df,ClaseSocial == 'Baja'), aes(x = p2.2.2.it1.Slice)) +  geom_bar(aes(y = (..count..)/sum(..count..))) + ggtitle("Chart 22 - Responses to Intelligent Public Transport, \n Lower Class") + xlab("Importance") + ylab("Percent") + scale_x_discrete(drop=FALSE) + scale_y_continuous(limits = c(0,0.5),breaks = c(.1,.2,.3,.4,.5,.6))

grid.arrange(inte_tr1_cla, inte_tr1_cma,inte_tr1_cm,inte_tr1_cmb,inte_tr1_b, ncol=3)
```

```{r}
ggplot(df, aes(factor(ClaseSocial), as.numeric(p2.2.2.it1.Slice))) + geom_boxplot() + ggtitle("Do we include this? It is catagorical")
```

######Intelligent Public Transport by Class - Statistical Difference
Given that the Lower Class was so distinctively different from the other four classes, we can expect the ANOVA tests will confirm a difference in mean score for intellegent public transport across class.

This is confirmed below, with the P-Value of 3.57e-06, indicating there is evidence to suggest there is a difference in means for the population.

```{r,echo=F}
inte_tr5_c_aov = aov(as.numeric(df$p2.2.2.it1.Slice)~df$ClaseSocial)
summary(inte_tr5_e_aov)
```

However, a more interesting question is if there is a difference in mean in the Upper, Upper Middle, Middle and Lower Middle Clases, which appear to have a similar distribution.

The ANOVA below indicates that there is no evidence to suggest there is difference in the mean scores between the four class groups. We do not reject the NULL.  This indicates that the person's class does not influence their opinion of the importance of Intelligent Public Transport.

The ANOVA parameters were
* The Null Hypothesis states that there is no difference between the mean score for the four class groups.
* The Alternative Hypothesis is that there is a difference between the mean score for each the class groups.
* The Confidence internal is 95%.

The resulting P-Value is 0.344 is over the critical. Therefore we do not reject the null hypothesis that the means are the same.


```{r,echo=F}
df_no_baja =subset(df, ClaseSocial != 'Baja')
df_no_baja$ClaseSocial = factor(df_no_baja$ClaseSocial)
table(df_no_baja$ClaseSocial)

inte_tr5_c_aov_no_baja = aov(as.numeric(df_no_baja$p2.2.2.it1.Slice)~df_no_baja$ClaseSocial)
summary(inte_tr5_c_aov_no_baja)
```

#################TENPLATE NOTES##################
Hi Team
So far, we have analysed one question, looking if there is difference between gender, age and class.
We will repeat this for every question.

Below, we do the same but on the scales scores
############################################

## Importance of Smart City initiatives in Mobility - Scaled Scores
### Overview of Scaling

The analysis above used the real scores. The real scores coded the responses from 1 to 5, with a Not Important  coded a 1 and a Very Important a 5.

Using real values can make it hard to determine the real opinion of a person. For example, if a person's average score to every question is 2, then a 3 is a higher score for them. However, for the same question, a person with an everage of 4 may also give a 3. Using real scores both responses are the same when in reality the opinion from the respondent has a very different meaning. 

```{r, echo=F, include=F}
slices = df[,grepl( "^p.*Slice$",names(df))]
slices = sapply(slices, as.numeric)
slices_mean = rowMeans(slices)
slices = as.data.frame(slices-slices_mean)
names(slices) =  paste(names(slices),"_scaled",sep = '')
df = as.data.frame(cbind(slices,df))


```

## Importance of Smart City initiatives in Mobility
### Overview
Participants were asked their opinion on howimportant six specific improvement were to them. They were asked to answer 1 if the improvement is not important and answer 5 if the initiative is Very Important. The six improvements were
* Intelligent Public Transport
* Automated Vehicle Access Restrictions and Tolls
* Intelligent Traffic Management
* Intelligent Fleet Management
* Parking Intelligence
* Electric Vehicle Infrastructure

Each improvement included examples of what this improvement might mean. 

###Responses
```{r, echo = F, include=F}
#Create the sum of scores for transport
df$slices_trans_sum_scaled = df$p2.2.2.it1.Slice_scaled +
                  df$p2.2.2.it2.Slice_scaled +
                  df$p2.2.2.it3.Slice_scaled +
                  df$p2.2.2.it4.Slice_scaled +
                  df$p2.2.2.it5.Slice_scaled + 
                  df$p2.2.2.it6.Slice_scaled

df$slices_trans_ave_scaled = df$p2.2.2.it2.Slice_scaled +
                  df$p2.2.2.it2.Slice_scaled +
                  df$p2.2.2.it3.Slice_scaled +
                  df$p2.2.2.it4.Slice_scaled +
                  df$p2.2.2.it5.Slice_scaled + 
                  df$p2.2.2.it6.Slice_scaled / 6

```

Using real scores, mobility and transport was identified as being mostly important to respondents. Chart 6 showed the histogram of the response scores, with a median of 3.8. Using the scaled scores, we see that average scaled score for transport and mobility is under 0. This means that they rated the transport and mobility improvement as less important as other themes.
```{r, echo=F}
inte_hist_slices_scaled = ggplot(df, aes(x = slices_trans_ave_scaled)) +  geom_histogram() + ggtitle("Chart 23 - Average Responses to Mobility Questions - Scaled") + xlab("Importance") + ylab("Count") + geom_vline(show.legend = TRUE,xintercept=0, linetype = "longdash")
inte_hist_slices_scaled 
```


Charts 24 to 29 below show the frequency of responses for each importance level. They indicate that Intelligent Public Transport is not as important to respondents than was indicated with the real scores.
 Electric Vehicle Infrastructure was again seen as being important. Again, initiatives focused on Access Restrictions appear to be the least popular. 
```{r,echo=F,fig.width=10}
inte_tr1_scaled = ggplot(df, aes(x = p2.1.2.it1.Slice_scaled)) +  geom_density() + ggtitle("Chart 24 - Scaled Responses to Intelligent Public Transport") + xlab("Importance - Scaled") + ylab("Percent") + scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

inte_tr2_scaled = ggplot(df, aes(x = p2.2.2.it2.Slice_scaled)) +  geom_density() + ggtitle("Chart 25 - Scaled Responses to Access Restrictions") + xlab("Importance - Scaled") + ylab("Percent")+ scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

inte_tr3_scaled = ggplot(df, aes(x = p2.2.2.it3.Slice_scaled)) +  geom_density() + ggtitle("Chart 26 - Scaled Responses to Intelligent Traffic Management") + xlab("Importance - Scaled") + ylab("Percent")+ scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

inte_tr4_scaled = ggplot(df, aes(x = p2.2.2.it4.Slice_scaled)) +  geom_density() + ggtitle("Chart 27 - Scaled Responses to Intelligent Fleet Management") + xlab("Importance - Scaled") + ylab("Percent")+ scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

inte_tr5_scaled = ggplot(df, aes(x = p2.2.2.it5.Slice_scaled)) +  geom_density() + ggtitle("Chart 28 - Scaled Responses to Parking Intelligence") + xlab("Importance - Scaled") + ylab("Percent")+ scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

inte_tr6_scaled = ggplot(df, aes(x = p2.2.2.it6.Slice_scaled)) +  geom_density() + ggtitle("Chart 29 - Scaled Responses to Electric Vehicle Infrastructure") + xlab("Importance - Scaled") + ylab("Percent")+ scale_x_continuous(breaks=seq(-4,4,1)) + xlim(-4, 4)

grid.arrange(inte_tr1_scaled, inte_tr2_scaled,inte_tr3_scaled,inte_tr4_scaled,inte_tr5_scaled,inte_tr6_scaled, ncol=2)

```

##Intelligent Public Transport - Scaled
Participants scaled scores on important intelligent public transport are now analysed. 

###Intelligent Public Transport by Gender - Sclaed
Before scaling, we saw that the responsed between men and women appeard different.
After scaling, we see that the responses appear similar.
```{r,echo=F}
ggplot(df,aes(x = p2.2.2.it1.Slice_scaled, color=sexo)) + geom_density() + ggtitle("Chart 30 - Scaled Responses to Intelligent Public Transport by Gender") + xlab("Importance - Scaled") + ylab("Count")
```

```{r}
ggplot(df, aes(factor(sexo), p2.2.2.it1.Slice_scaled)) + geom_boxplot()
```

######Intelligent Public Transport by Gender - Statistical Difference of the Scaled Values
This apparent difference is now tested statistically with the aim of determining if the difference in the sample can be hypothesised against the population as a whole.

The T-Test below indicates that there is difference in the scaled mean scores between men and women over the population. This indicates that men and women differ in their opinion of the importance of Intelligent Public Transport.

The T-Test's parameters are
* The Null Hypothesis states that there is no difference between the mean score for men and women.
* The Alternative Hypothesis is that there is a difference between the mean score for men and women.
* The Confidence internal is 95%.

The resulting P-Value is 0.01502675 which is under our critical. Therefore we reject the null hypothesis that the means are the same. 
```{r,echo=F}
inte_tr5_g_ttest_scaled = t.test(as.numeric(df$p2.2.2.it1.Slice_scaled)~df$sexo)
inte_tr5_g_ttest_scaled$p.value
```


###Intelligent Public Transport by Age - Scaled
Using scaled scores, the distribution of responses across age appears to be more similar.

```{r,echo=F}
ggplot(df,aes(x = p2.2.2.it1.Slice_scaled, color=edad)) + geom_density() + ggtitle("Chart 31 - Scaled Responses to Intelligent Public Transport by Age") + xlab("Importance - Scaled") + ylab("Count")
```


```{r}
ggplot(df, aes(factor(edad), p2.2.2.it1.Slice_scaled)) + geom_boxplot()
```

###Intelligent Public Transport by Age - Statistical Difference of the Scaled Values
This is now tested statistically with the aim of determining if the difference in the sample can be hypothesised against the population as a whole.

The ANOVA below provides evidence that the mean scores between the age groups over the population is the same. This indicates that the person's age does not influence their opinion of the importance of Intelligent Public Transport.

The ANOVA parameters were
* The Null Hypothesis states that there is no difference between the mean scaled score for each age group.
* The Alternative Hypothesis is that there is a difference between the mean score for each age group.
* The Confidence internal is 95%.

The resulting P-Value is 0.377 so we do not reject the null hypothesis using scaled values.
```{r,echo=F}
inte_tr5_e_aov_scaled = aov(df$p2.2.2.it1.Slice_scaled~df$edad)
summary(inte_tr5_e_aov_scaled)
```

This is different to the results from the same test when using the real values.


###Intelligent Public Transport by Class - Scaled
Across the classes, there were only small differences in opinion about the importance of intelligent public transport. Chart 32 shows similar distributions for the Upper, Upper Middle, Middle and Lower Middles clases. The outlier, again, is the lower class. The result in this class group is likely influenced by the low number of total respondents in this group (15 respondents). 

```{r,echo=F}
ggplot(df,aes(x = p2.2.2.it1.Slice_scaled, color=ClaseSocial)) + geom_density() + ggtitle("Chart 32 - Scaled Responses to Intelligent Public Transport by Age") + xlab("Importance - Scaled") + ylab("Count")
```


```{r}
ggplot(df, aes(factor(ClaseSocial), p2.2.2.it1.Slice_scaled)) + geom_boxplot()
```

###Intelligent Public Transport by Class - Statistical Difference of the Scaled Values

Testing for significance of the different for the population, we see that the we do not have enough evidence to reject the null hypothesis.

The resulting P-Value is 0.126 so we do not reject the null hypothesis using scaled values.
```{r,echo=F}
inte_tr5_c_aov_scaled = aov(df$p2.2.2.it1.Slice_scaled~df$ClaseSocial)
summary(inte_tr5_c_aov_scaled)
```

This is different to the results from the same test when using the real values.
